---
title: "Penguins Anova"
author: "Madeline Berger"
date: "11/6/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Load packages and read in the penguins.csv data

```{r, message = FALSE}
library(tidyverse)
library(car)
library(onewaytests)

penguins <- read_csv("penguins.csv")
```

Our question:

Is there a significant difference in mean flipper length for female penguins by species (Chinstrap, Gentoo, Adelie)?

2. Do some exploring (already in tidyverse)

New functions: with + table for easy counting over multiple factors

Update the species name using case_when 

```{r}

counts <- with(penguins, table(species, sex))

penguins2 <- penguins %>% 
  mutate(common_name =
           case_when(species == "Chinstrap penguin (Pygoscelis antarctica)" ~ "Chinstrap",
            species == "Gentoo penguin (Pygoscelis papua)" ~ "Gentoo", 
            species == "Adelie Penguin (Pygoscelis adeliae)" ~ "Adelie" )) %>% 
  select(-species) %>% 
  filter(sex == "FEMALE")

penguins2



```

-Exploratory graphs
-Summary statistics
-Levene's test for equal variances
-one-way ANOVA
-post-hoc testing

```{r}
#Exploratory Graphs 

hists <- ggplot(penguins2, aes(x = flipper_length)) +
  geom_histogram(aes(fill = common_name))+
  facet_wrap(~common_name)

hists


qq <- ggplot(penguins2, aes(sample = flipper_length))+
               geom_qq()+
               facet_wrap(~common_name)

qq


#Levene's test for equal variances (>2 groups, if you have two groups, use the F-test for equal variances)

#We'll use the function leveneTest from the 'car' package

#H0: Variances are equal
#HA: Variances are unequal 


penguin_levene <- leveneTest(flipper_length ~ common_name, data = penguins2)
penguin_levene

#We retain the null hypothesis of equal variances ( p = 0.06)

var_table <- penguins2 %>% 
  group_by(common_name) %>% 
  summarize(
    var_flip = var(flipper_length)
  )

var_table

#these are close enough to use an ANOVA because largest is <4x greater than smallest
```



