---
title: "Penguins Anova"
author: "Madeline Berger"
date: "11/6/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Load packages and read in the penguins.csv data

```{r, message = FALSE}
library(tidyverse)
library(car)
library(onewaytests)

penguins <- read_csv("penguins.csv")
```

Our question:

Is there a significant difference in mean flipper length for female penguins by species (Chinstrap, Gentoo, Adelie)?

2. Do some exploring (already in tidyverse)

New functions: with + table for easy counting over multiple factors

Update the species name using case_when 

```{r}

counts <- with(penguins, table(species, sex))

penguins2 <- penguins %>% 
  mutate(common_name =
           case_when(
            species == "Chinstrap penguin (Pygoscelis antarctica)" ~ "Chinstrap",
            species == "Gentoo penguin (Pygoscelis papua)" ~ "Gentoo", 
            species == "Adelie Penguin (Pygoscelis adeliae)" ~ "Adelie" )) %>% 
  select(-species) %>% 
  filter(sex == "FEMALE")

penguins2



```

-Exploratory graphs
-Summary statistics
-Levene's test
